\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{array}

% ── Color definitions ──
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{javadoc}{rgb}{0.25,0.35,0.55}

% ── Code style ──
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\small,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    numbers=left,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=4,
    frame=single,
    rulecolor=\color{codegray},
    xleftmargin=2em,
    framexleftmargin=1.5em,
}
\lstset{style=mystyle}

% ── Java language definition improvements ──
\lstdefinelanguage{JavaImproved}{
    language=Java,
    morekeywords={@Override,@SuppressWarnings},
    sensitive=true,
}

\title{\textbf{CN-Market Stock Market Plugin}\\[0.5em]
\large Technical Documentation \& Developer Guide}
\author{CraftNepal Development Team}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

% ── Helper for breaking paths in tables ──
\newcommand{\apipath}[1]{\path{#1}}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Introduction}
% ══════════════════════════════════════════════════════════════════════════════

The CN-Market plugin is a Spigot/Paper 1.21.x Minecraft server plugin that
provides a persistent market world with player-owned shops, admin shops,
currency exchange, and---since version 1.1.4---a full real-time stock market
system with web-based trading.

This document covers the stock market subsystem: its architecture,
authentication model, REST and WebSocket APIs, order matching engine,
candle aggregation, and the companion React frontend.

The stock market allows players to trade virtual ``shares'' backed by
in-game item tickers (e.g.\ DIAMOND, IRON\_INGOT). All trades settle
against the player's Vault economy balance in real time. No physical items
move; the system is a pure speculation layer on top of the existing shop
economy.

% ══════════════════════════════════════════════════════════════════════════════
\chapter{System Architecture}
% ══════════════════════════════════════════════════════════════════════════════

\section{Component Overview}

The stock market system consists of the following components:

\begin{description}
\item[StockMarketEngine] Core singleton that maintains the in-memory order book,
  executes trades, manages portfolios, and persists all state to SQLite.
\item[EmbeddedServer] JDK \texttt{com.sun.net.httpserver.HttpServer} running on a
  configurable port (default 8080). Serves REST JSON endpoints for
  authentication, market data, and trading.
\item[WebSocketManager] Separate server (default port 8081) that implements the
  RFC~6455 WebSocket protocol. Broadcasts real-time ticker snapshots, trade
  executions, and order book updates.
\item[ApiKeyManager] Handles API key generation (PBKDF2WithHmacSHA256, 120k
  iterations), session tokens, TOTP setup, lockout logic, and backup code
  verification.
\item[TwoFactorAuth] RFC~6238 TOTP implementation using HMAC-SHA1 and
  Base32-encoded secrets.
\item[CandleAggregator] Background task that builds OHLCV candlestick data
  from the trade history at five interval granularities.
\item[RateLimiter] Sliding-window rate limiter applied to all REST and
  WebSocket traffic.
\item[transform.ts] Shared TypeScript utility that normalizes all
  snake\_case API and WebSocket responses to camelCase,
  providing a consistent interface to all frontend components.
\end{description}

\section{Data Flow}

\begin{enumerate}
\item A player generates an API key in-game: \texttt{/market apikey generate}.
  The plaintext key is shown once, its PBKDF2 hash is stored in SQLite.
 \item The player visits the web frontend and enters the API key on the login page.
\item The frontend calls \texttt{POST /api/v1/auth/step1} with the key. The
  server resolves the key to a UUID, checks expiration and lockout status,
  and returns the UUID plus TOTP setup data if first-time setup is needed.
\item The frontend calls \texttt{POST /api/v1/auth/step2} with the UUID
  and a TOTP code from the player's authenticator app. On success, a session
  cookie (\texttt{market\_session}) is set and a session token is returned.
\item All subsequent API calls carry the session cookie via
  \texttt{credentials: 'include'}. The server resolves the session to a UUID
  and executes the requested operation (place order, cancel order, query
  portfolio, etc.).
\item All API and WebSocket responses use snake\_case field names. The
  frontend's \texttt{transformKeys()} utility normalizes them to camelCase
  before they reach React components.
\item When a trade executes, \texttt{StockMarketEngine} calls
  \texttt{broadcastTrades()}, which pushes the trade event to
  \texttt{WebSocketManager}. The WebSocket server broadcasts to all
  subscribed clients.
\item A separate tick loop runs every 60 seconds: evaluate stop-loss and
  take-profit orders, aggregate OHLCV candles, clean up old data.
\end{enumerate}

\section{Database Schema}

All persistent state lives in a single SQLite file at
\texttt{plugins/Market/market.db}. The stock-market tables are:

\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{7.5cm}}
\toprule
\textbf{Table} & \textbf{Purpose} & \textbf{Key Columns} \\
\midrule
\texttt{api\_keys} & API key hashes, TOTP, sessions & uuid, key\_hash, totp\_secret, session\_token \\
\texttt{stock\_orders} & All orders (open/filled/cancelled) & id, ticker, type, side, price, quantity, status \\
\texttt{stock\_trades} & Executed trade log & id, ticker, price, quantity, buyer, seller, timestamp \\
\texttt{stock\_portfolios} & Player share holdings & uuid, ticker, shares, avg\_entry\_price \\
\texttt{stock\_candles} & OHLCV aggregated candles & ticker, interval, open\_time, o/h/l/c, volume \\
\bottomrule
\end{tabular}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Stock Market Engine}
% ══════════════════════════════════════════════════════════════════════════════

\section{File Location}

All stock market engine code resides in:
\begin{quote}
\texttt{src/main/java/net/craftnepal/market/stock/}
\end{quote}

The main engine is \texttt{StockMarketEngine.java} (\textasciitilde990 lines).

\section{Order Types}

The engine supports four order types, defined in the \texttt{OrderType} enum
at line~24:

\begin{lstlisting}[language=Java, caption=Order types (StockMarketEngine.java:24)]
public enum OrderType {
    MARKET, LIMIT, STOP_LOSS, TAKE_PROFIT
}
\end{lstlisting}

\begin{description}
\item[MARKET] Executes immediately against the best available opposite orders
  in the book. No price limit is required.
\item[LIMIT] Executes only at the specified price or better. If not fully
  filled, the remainder sits in the order book.
\item[STOP\_LOSS] A sell order that sits in the book until the market price
  drops to or below the stop price. When triggered, it converts to a MARKET
  sell and executes immediately.
\item[TAKE\_PROFIT] A sell order that sits in the book until the market price
  rises to or above the target price. When triggered, it converts to a MARKET
  sell.
\end{description}

Price clamping is enforced for LIMIT orders at lines~224--229:

\begin{lstlisting}[language=Java, caption=Price clamping (StockMarketEngine.java:224-229)]
if (type == OrderType.LIMIT && price > 0) {
    double maxAllowed = referencePrice * 1.20;
    double minAllowed = referencePrice * 0.80;
    if (price > maxAllowed) price = maxAllowed;
    if (price < minAllowed) price = minAllowed;
}
\end{lstlisting}

\section{Order Matching Algorithm}

The engine uses an in-memory order book implemented with
\texttt{ConcurrentHashMap<String, NavigableMap<Double, List<Order>>>}
(lines~126--127):

\begin{lstlisting}[language=Java, caption=Order book data structures (StockMarketEngine.java:126-127)]
private static final ConcurrentHashMap<String, NavigableMap<Double, List<Order>>>
    bidsByTicker = new ConcurrentHashMap<>();
private static final ConcurrentHashMap<String, NavigableMap<Double, List<Order>>>
    asksByTicker = new ConcurrentHashMap<>();
\end{lstlisting}

Bids are stored in descending order (highest bid first), asks in ascending
order (lowest ask first). The matching logic for a buy market order
(\texttt{matchBuyMarket}, line~325) iterates ask levels from low to high,
matching as much quantity as possible at each price level. For limit orders
(\texttt{matchBid}, line~428), matching stops when the ask price exceeds the
bid price.

\subsection{Price Discovery}

When a trade executes, the trade price is recorded as the last price for that
ticker (line~514):

\begin{lstlisting}[language=Java, caption=Last price update (StockMarketEngine.java:513-514)]
// Update last price
lastPrices.put(buyOrder.ticker, tradePrice);
\end{lstlisting}

If no trades exist for a ticker, the engine falls back to
\texttt{DynamicPriceManager.getDynamicPrice()} which provides a fundamental
value based on the item's shop price history.

\section{Stop-Order Evaluation}

The \texttt{evaluateStopOrders()} method (line~777) runs on a 60-second async
timer from \texttt{Market.java}. It queries all OPEN stop-loss and
take-profit orders from the database, checks the current market price against
each order's stop price, and triggers matching orders as MARKET orders:

\begin{lstlisting}[language=Java, caption=Stop-order trigger logic (StockMarketEngine.java:795-803)]
boolean shouldTrigger = false;
if (order.type == OrderType.STOP_LOSS) {
    if (order.side == OrderSide.SELL && currentPrice <= order.stopPrice) {
        shouldTrigger = true;
    }
} else if (order.type == OrderType.TAKE_PROFIT) {
    if (order.side == OrderSide.SELL && currentPrice >= order.stopPrice) {
        shouldTrigger = true;
    }
}
\end{lstlisting}

\section{Portfolio Management}

Player share holdings are tracked in two maps (lines~128--129):

\begin{lstlisting}[language=Java, caption=Portfolio state (StockMarketEngine.java:128-129)]
private static final ConcurrentHashMap<String, HashMap<String, Integer>>
    playerShares = new ConcurrentHashMap<>();
private static final ConcurrentHashMap<String, HashMap<String, Double>>
    playerAvgPrice = new ConcurrentHashMap<>();
\end{lstlisting}

The \texttt{getPortfolio()} method (line~621) computes per-holding P\&L and
returns a structured map with total value, cost, and percentage returns.

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Authentication System}
% ══════════════════════════════════════════════════════════════════════════════

\section{API Key Lifecycle}

\subsection{Generation}

Keys are generated by \texttt{ApiKeyManager.generateKey()}:

\begin{lstlisting}[language=Java, caption=API key generation (ApiKeyManager.java)]
public static String[] generateKey(String uuid) {
    byte[] keyBytes = new byte[32];
    RANDOM.nextBytes(keyBytes);
    StringBuilder key = new StringBuilder("mk_");
    for (byte b : keyBytes) key.append(String.format("%02x", b & 0xff));
    String plainKey = key.toString();
    String hash = hashKey(plainKey);
    // store hash in DB, return plaintext key
}
\end{lstlisting}

The plaintext key (format: \texttt{mk\_} followed by 64 hex characters) is
displayed to the player exactly once via the in-game command and is never
persisted. The hash uses PBKDF2WithHmacSHA256 with 120,000 iterations.

\subsection{Expiration and Renewal}

Keys expire after 7 days. The player can renew via
\texttt{/market apikey renew} before expiration. Expired keys return 401
from the API.

\subsection{Revocation}

\texttt{/market apikey revoke} immediately deletes the key hash from the
database, invalidating all active sessions.

\section{Two-Factor Authentication (TOTP)}

When a player first authenticates through the website, the server checks
whether TOTP has been set up. If not, it generates a secret and returns a
provisioning URL for the authenticator app:

\begin{lstlisting}[language=Java, caption=TOTP setup response (EmbeddedServer.java:127-135)]
if (!data.totpEnabled) {
    String totpSecret = TwoFactorAuth.generateSecret();
    String[] backupCodes = TwoFactorAuth.generateBackupCodes();
    String qrUrl = TwoFactorAuth.getQRCodeURL(getPlayerName(uuid), totpSecret);
    resp.put("totp_setup_needed", true);
    resp.put("totp_secret", totpSecret);
    resp.put("qr_code_url", qrUrl);
    resp.put("backup_codes", String.join(", ", backupCodes));
    ApiKeyManager.setupTOTP(uuid, totpSecret, backupCodes);
}
\end{lstlisting}

The TOTP implementation follows RFC~6238 using HMAC-SHA1 and 30-second
time steps. Backup codes are hashed with the same PBKDF2 function and stored
as a JSON array in the \texttt{backup\_codes} column.

\section{Session Management}

After step~2, a session token is created (line~178):

\begin{lstlisting}[language=Java, caption=Session creation (EmbeddedServer.java:178-183)]
String sessionToken = ApiKeyManager.createSession(uuid);
Map<String, Object> resp = new HashMap<>();
resp.put("session_token", sessionToken);
resp.put("expires_at", System.currentTimeMillis() + (24L * 60L * 60L * 1000L));
setSessionCookie(exchange, sessionToken, 86400);
\end{lstlisting}

Sessions are stored in the \texttt{api\_keys} table as
\texttt{session\_token} and \texttt{session\_expires\_at}. A new login
overwrites the previous session, providing single-concurrent-session
semantics.

\section{Lockout Policy}

Five consecutive failed TOTP attempts triggers a 15-minute lockout
(\texttt{locked\_until} column). Ten failures permanently revokes the key.
Attempts are tracked per UUID in the \texttt{failed\_attempts} column.

\section{Rate Limiting}

The \texttt{RateLimiter} class uses a sliding-window algorithm:

\begin{lstlisting}[language=Java, caption=Rate limiter core (RateLimiter.java)]
public static boolean allow(String key, int maxRequests, long windowMs) {
    long now = System.currentTimeMillis();
    ArrayDeque<Long> log = logs.computeIfAbsent(key, k -> new ArrayDeque<>());
    synchronized (log) {
        while (!log.isEmpty() && log.peekFirst() < now - windowMs)
            log.pollFirst();
        if (log.size() >= maxRequests) return false;
        log.addLast(now);
        return true;
    }
}
\end{lstlisting}

Default configuration: 120 requests per 60-second window per IP/UUID.
WebSocket clients are limited to 30 messages per 10 seconds.

% ══════════════════════════════════════════════════════════════════════════════
\chapter{REST API}
% ══════════════════════════════════════════════════════════════════════════════

\section{Server Details}

The REST server is implemented by \texttt{EmbeddedServer.java} using
JDK's built-in \texttt{com.sun.net.httpserver.HttpServer}. It listens on
port 8080 by default (configurable in config.yml).

\section{Authentication Endpoints}

\begin{longtable}{>{\raggedright\arraybackslash}p{1.8cm}>{\raggedright\arraybackslash}p{6cm}>{\raggedright\arraybackslash}p{7cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Description} \\
\midrule
\endhead
POST & \apipath{/api/v1/auth/step1} & Submit API key; returns session token.
  Body: \texttt{\{key: "mk\_..."\}}. \\
POST & \apipath{/api/v1/auth/step2} & Submit TOTP code.
  Body: \texttt{\{uuid, code\}}. Returns \texttt{session\_token} cookie. \\
POST & \apipath{/api/v1/auth/logout} & Destroy current session. \\
GET & \apipath{/api/v1/auth/status} & Check authentication status. \\
\bottomrule
\end{longtable}

\section{Market Data Endpoints}

\begin{longtable}{>{\raggedright\arraybackslash}p{1.8cm}>{\raggedright\arraybackslash}p{6cm}>{\raggedright\arraybackslash}p{7cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Description} \\
\midrule
\endhead
GET & \apipath{/api/v1/tickers} & All ticker snapshots sorted by absolute
  price change. \\
GET & \apipath{/api/v1/ticker/{ticker}} & Single ticker detail.
  E.g.\ \apipath{/api/v1/ticker/DIAMOND}. \\
GET & \apipath{/api/v1/orderbook/{ticker}/{depth}} & Bid/ask levels with
  quantities and order counts. \\
GET & \apipath{/api/v1/trades/{ticker}/{limit}} & Recent trade history. \\
GET & \apipath{/api/v1/candles/{ticker}/{interval}/{limit}} & OHLCV
  candle data. Intervals: 1m, 5m, 15m, 1h, 1d. \\
\bottomrule
\end{longtable}

The \texttt{TickersHandler} (line~264) constructs a JSON array of all ticker
snapshots:

\begin{lstlisting}[language=Java, caption=Tickers response builder (EmbeddedServer.java:273-291)]
List<TickerSnapshot> snapshots = StockMarketEngine.getAllTickers();
List<Map<String, Object>> list = new ArrayList<>();
for (TickerSnapshot s : snapshots) {
    Map<String, Object> m = new LinkedHashMap<>();
    m.put("ticker", s.ticker);
    m.put("last_price", s.lastPrice);
    m.put("bid", s.bidPrice);
    m.put("ask", s.askPrice);
    m.put("spread", s.spread);
    m.put("change_24h_pct", Math.round(s.change24h * 100.0) / 100.0);
    m.put("volume_24h", s.volume24h);
    m.put("high_24h", s.high24h);
    m.put("low_24h", s.low24h);
    list.add(m);
}
\end{lstlisting}

\section{Trading Endpoints}

\begin{longtable}{>{\raggedright\arraybackslash}p{1.8cm}>{\raggedright\arraybackslash}p{6cm}>{\raggedright\arraybackslash}p{7cm}}
\toprule
\textbf{Method} & \textbf{Path} & \textbf{Description} \\
\midrule
\endhead
GET & \apipath{/api/v1/orders} & List open orders for authenticated player. \\
POST & \apipath{/api/v1/orders} & Place an order. Body:
  \texttt{\{ticker, side, type, price?, quantity\}} \\
DELETE & \apipath{/api/v1/order/{id}} & Cancel an open order. \\
GET & \apipath{/api/v1/portfolio} & Portfolio holdings with P\&L. \\
GET & \apipath{/api/v1/balance} & Player's Vault balance. \\
\bottomrule
\end{longtable}

The \texttt{OrdersHandler} POST path (line~508) parses the request body and
delegates to \texttt{StockMarketEngine.placeOrder()}:

\begin{lstlisting}[language=Java, caption=Order placement (EmbeddedServer.java:508-543)]
Map<String, String> body = parseForm(exchange);
String ticker = body.get("ticker");
String side = body.get("side");
String type = body.get("type");
String priceStr = body.get("price");
String qtyStr = body.get("quantity");

OrderType orderType = OrderType.valueOf(type.toUpperCase());
OrderSide orderSide = OrderSide.valueOf(side.toUpperCase());
double price = priceStr != null ? Double.parseDouble(priceStr) : 0;
int quantity = Integer.parseInt(qtyStr);

OrderResult result = StockMarketEngine.placeOrder(
    uuid, ticker, orderType, orderSide, price, quantity);
\end{lstlisting}

\section{CORS and Error Handling}

Every handler begins with \texttt{handleCors(exchange)} which adds
\texttt{Access-Control-Allow-Origin: *} and handles OPTIONS preflight
requests. Errors are returned as JSON with an \texttt{error} field and
\texttt{success: false}.

% ══════════════════════════════════════════════════════════════════════════════
\chapter{WebSocket Protocol}
% ══════════════════════════════════════════════════════════════════════════════

\section{Server Details}

\texttt{WebSocketManager.java} implements RFC~6455 on a separate port
(default 8081). The implementation is self-contained---no external
dependencies---using only JDK classes.

\section{Connection}

In development, the client connects directly:
\begin{quote}
\texttt{ws://localhost:8081}
\end{quote}

In production, the nginx reverse proxy forwards \texttt{/ws} on the same
origin to port 8081, so the client connects via:
\begin{quote}
\texttt{wss://market.craftnepal.net/ws}
\end{quote}

The frontend determines the URL automatically using
\texttt{location.protocol} and \texttt{location.host} in production builds.

The server performs the standard WebSocket upgrade handshake:

\begin{lstlisting}[language=Java, caption=WebSocket handshake (WebSocketManager.java)]
MessageDigest sha1 = MessageDigest.getInstance("SHA-1");
sha1.update(key.getBytes());
sha1.update(MAGIC_GUID.getBytes());
acceptKey = Base64.getEncoder().encodeToString(sha1.digest());

String response = "HTTP/1.1 101 Switching Protocols\r\n" +
    "Upgrade: websocket\r\n" +
    "Connection: Upgrade\r\n" +
    "Sec-WebSocket-Accept: " + acceptKey + "\r\n" +
    "Access-Control-Allow-Origin: *\r\n" + "\r\n";
out.write(response.getBytes());
\end{lstlisting}

\section{Subscription Protocol}

After connecting, the client sends JSON messages to subscribe to channels:

\begin{lstlisting}[language=TeX, caption=Client subscribe message]
{"type":"subscribe","channel":"tickers"}
{"type":"subscribe","channel":"trades.DIAMOND"}
{"type":"subscribe","channel":"orderbook.DIAMOND"}
\end{lstlisting}

Unsubscribe follows the same pattern:

\begin{lstlisting}[language=TeX, caption=Client unsubscribe message]
{"type":"unsubscribe","channel":"trades.DIAMOND"}
\end{lstlisting}

\section{Broadcast Channels}

\begin{longtable}{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{7cm}>{\raggedright\arraybackslash}p{4cm}}
\toprule
\textbf{Channel} & \textbf{Content} & \textbf{Frequency} \\
\midrule
\endhead
\texttt{tickers} & All ticker snapshots (price, change, volume, high/low) & Every 5 seconds \\
\texttt{trades} & All executed trades (id, ticker, price, qty, timestamp) & On every match \\
\texttt{trades.\{TICKER\}} & Per-ticker trade feed & On every match \\
\texttt{orderbooks} & All order book depth (top 10 levels) & On every trade \\
\texttt{orderbook.\{TICKER\}} & Per-ticker depth & On every trade \\
\bottomrule
\end{longtable}

\section{Message Formats}

Ticker broadcast:

\begin{lstlisting}[language=TeX, caption=WebSocket ticker message]
{
  "type": "tickers",
  "data": [
    {"ticker":"DIAMOND","last_price":150.25,"bid":149.00,
     "ask":151.50,"change_24h_pct":2.34,"volume_24h":1200,
     "high_24h":155.00,"low_24h":145.50}
  ]
}
\end{lstlisting}

Trade broadcast:

\begin{lstlisting}[language=TeX, caption=WebSocket trade message]
{
  "type": "trade",
  "data": {
    "id": "trd_a1b2c3d4e5f6",
    "ticker": "DIAMOND",
    "price": 150.25,
    "quantity": 10,
    "buyer_uuid": "00000000-0000-0000-0000-000000000000",
    "seller_uuid": "00000000-0000-0000-0000-000000000000",
    "timestamp": 1700000000000
  }
}
\end{lstlisting}

Order book broadcast:

\begin{lstlisting}[language=TeX, caption=WebSocket order book message]
{
  "type": "orderbook",
  "ticker": "DIAMOND",
  "data": {
    "bids": [{"price":150.00,"quantity":50,"orders":3}],
    "asks": [{"price":151.00,"quantity":30,"orders":2}]
  }
}
\end{lstlisting}

\section{Keepalive}

The server sends a WebSocket ping frame to every connected client every
30 seconds. Clients should respond with a pong. Dead connections are
cleaned up automatically.

% ══════════════════════════════════════════════════════════════════════════════
\chapter{OHLCV Aggregation Engine}
% ══════════════════════════════════════════════════════════════════════════════

\section{Purpose}

The \texttt{CandleAggregator} class converts raw trade data into
standardized candlestick data for charting. It runs every 60 seconds via
the Bukkit scheduler.

\section{Intervals}

Five interval granularities are supported:

\begin{tabular}{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
\textbf{Interval} & \textbf{Period} & \textbf{Retention} \\
\midrule
1m & 60 seconds & 24 hours \\
5m & 5 minutes & 7 days \\
15m & 15 minutes & 30 days \\
1h & 1 hour & 90 days \\
1d & 1 day & Forever \\
\bottomrule
\end{tabular}

\section{Aggregation Algorithm}

For each interval, the aggregator queries trades since the last candle's
close time, groups them by time bucket (\texttt{timestamp - (timestamp \% intervalMs)}),
and computes OHLCV for each bucket:

\begin{lstlisting}[language=Java, caption=Candle building (CandleAggregator.java)]
static class CandleBuilder {
    double open, high, low, close;
    int volume, tradeCount;
    boolean initialized;

    void add(double price, int qty) {
        if (!initialized) {
            open = high = low = close = price;
            initialized = true;
        } else {
            if (price > high) high = price;
            if (price < low) low = price;
            close = price;
        }
        volume += qty;
        tradeCount++;
    }
}
\end{lstlisting}

Candles are upserted into the \texttt{stock\_candles} table using
\texttt{INSERT OR REPLACE} with a composite primary key of
\texttt{(ticker, interval, open\_time)}.

\section{Query}

The \texttt{CandlesHandler} REST endpoint at
\texttt{GET /api/v1/candles/\{ticker\}/\{interval\}/\{limit\}} returns sorted
candle data for the chart:

\begin{lstlisting}[language=Java, caption=Candle query (CandleAggregator.java)]
public static List<Candle> getCandles(String ticker, String interval, int limit) {
    String sql = "SELECT * FROM stock_candles WHERE ticker = ? AND interval = ? " +
                 "ORDER BY open_time DESC LIMIT ?";
    // ... execute, reverse into ascending order ...
}
\end{lstlisting}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Admin Commands}
% ══════════════════════════════════════════════════════════════════════════════

All stock market admin commands require the \texttt{market.admin} permission
and are accessed under: \texttt{/market admin stock <subcommand>}.

\section{Pause}

Pauses the stock market engine. All order matching and stop-order evaluation
stops immediately. New orders return an error with message
``Stock market is currently paused by an admin.''

\begin{lstlisting}[language=sh, caption=Usage]
/market admin stock pause [reason]
\end{lstlisting}

Implementation (\texttt{StockMarketEngine.java}):

\begin{lstlisting}[language=Java, caption=Pause implementation]
public static void pause() {
    paused = true;
    Bukkit.getLogger().warning("[Market] Stock market PAUSED.");
}
\end{lstlisting}

\section{Resume}

Resumes the stock market engine after a pause. Matching and stop-order
evaluation resume on the next tick cycle.

\begin{lstlisting}[language=sh, caption=Usage]
/market admin stock resume
\end{lstlisting}

\begin{lstlisting}[language=Java, caption=Resume implementation]
public static void resume() {
    paused = false;
    Bukkit.getLogger().info("[Market] Stock market RESUMED.");
}
\end{lstlisting}

\section{Inject Test Trade}

Injects a fake trade directly into the system without going through the
order book. This sets the last price for the ticker and creates a trade
record, which is broadcast to WebSocket subscribers. Useful for testing
the full pipeline (database, REST API, WebSocket, frontend chart) without
player interaction.

\begin{lstlisting}[language=sh, caption=Usage]
/market admin stock inject <ticker> <price> <quantity>
\end{lstlisting}

Example:
\begin{lstlisting}[language=sh, caption=Example]
/market admin stock inject DIAMOND 150.25 10
\end{lstlisting}

Implementation (\texttt{StockMarketEngine.java}):
\begin{lstlisting}[language=Java, caption=Inject trade implementation]
public static Trade injectTrade(String ticker, double price, int quantity) {
    if (!loaded) return null;
    ticker = ticker.toUpperCase();
    lastPrices.put(ticker, price);
    Trade trade = new Trade(
        generateId("trd_"), ticker, price, quantity,
        "00000000-0000-0000-0000-000000000000",
        "00000000-0000-0000-0000-000000000000",
        "injected", "injected", System.currentTimeMillis()
    );
    saveTrade(trade);
    broadcastTrades(List.of(trade));
    return trade;
}
\end{lstlisting}

\section{Status}

Displays current stock market engine status including pause state, open order
count, and 24-hour trade count.

\begin{lstlisting}[language=sh, caption=Usage]
/market admin stock status
\end{lstlisting}

Sample output:
\begin{lstlisting}[language=sh, caption=Sample status output]
--- Stock Market Status ---
Engine: RUNNING
Open orders: 12
Trades (24h): 45
\end{lstlisting}

\section{Complete Subcommand Registration}

The \texttt{StockCommand} nested command (\texttt{StockCommand.java})
registers all four subcommands:

\begin{lstlisting}[language=Java, caption=StockCommand registration]
public class StockCommand extends NestedCommand {
    public StockCommand() {
        registerSubCommand(new Pause());
        registerSubCommand(new Resume());
        registerSubCommand(new Inject());
        registerSubCommand(new Status());
    }
    @Override
    public String getRequiredPermission() { return "market.admin"; }
    @Override
    public String getName() { return "stock"; }
}
\end{lstlisting}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Frontend Application}
% ══════════════════════════════════════════════════════════════════════════════

\section{Technology Stack}

\begin{description}
\item[Build] Vite 6 + TypeScript 5
\item[UI] React 18, React Router 6
\item[Charting] TradingView Lightweight Charts 4
\item[Styling] Tailwind CSS 3 (Catppuccin dark theme)
\end{description}

\section{Project Structure}

\begin{verbatim}
stock-website/
+-- src/
    +-- api/
    |   +-- client.ts       # fetch wrapper with cookie auth (credentials:include)
    |   +-- auth.ts         # step1, step2, status, logout
    |   +-- market.ts       # tickers, orderbook, trades, orders, portfolio
    |   +-- websocket.ts    # WsClient with auto-reconnect + key transform
    |   +-- transform.ts    # snake_case to camelCase normalizer
    +-- store/
    |   +-- auth.tsx        # AuthContext + AuthProvider
    +-- pages/
    |   +-- Login.tsx       # API key entry
    |   +-- Verify2FA.tsx   # TOTP code entry
    |   +-- Dashboard.tsx   # Main trading interface
    |   +-- Portfolio.tsx   # Holdings with P&L
    +-- components/
    |   +-- Layout.tsx      # Header + router outlet
    |   +-- Header.tsx      # Navigation + logout
    |   +-- TickerList.tsx  # Searchable ticker sidebar
    |   +-- Chart.tsx       # Candlestick chart with interval selector
    |   +-- OrderBook.tsx   # Bid/ask levels with depth bars
    |   +-- TradeHistory.tsx# Recent trades feed
    |   +-- OrderForm.tsx   # Buy/Sell with Market/Limit/Stop types
    |   +-- OrderList.tsx   # Open orders table with cancel
    +-- types/index.ts      # All TypeScript interfaces
\end{verbatim}

\section{Key Components}

\subsection{WebSocket Client (\texttt{api/websocket.ts})}

The \texttt{WsClient} class provides automatic reconnection with a 5-second
backoff, typed event handling, and subscribe/unsubscribe:

\begin{lstlisting}[language=Java, caption=WebSocket client class]
export class WsClient {
  private ws: WebSocket | null = null;
  private handlers = new Map<string, Set<WsMessageHandler>>();
  private reconnectTimer: ReturnType<typeof setTimeout> | null = null;

  subscribe(channel: string) {
    this.send({ type: 'subscribe', channel });
  }

  on(type: string, handler: WsMessageHandler) {
    if (!this.handlers.has(type)) this.handlers.set(type, new Set());
    this.handlers.get(type)!.add(handler);
    return () => this.handlers.get(type)?.delete(handler);
  }
}
\end{lstlisting}

\subsection{Dashboard Layout}

The Dashboard (\texttt{pages/Dashboard.tsx}) renders a multi-panel layout:

\begin{verbatim}
+--------------------------------------------------------------+
| Header:  CN Market | Trade | Portfolio  | Player | Logout    |
+----------+------------------------------+--------------------+
| Ticker   |     Candlestick Chart        |   Order Book       |
| List     |     (Lightweight Charts)     |   (bids / asks)    |
| (sorted  |     + interval selector     +--------------------+
|  by |%|) |                              |   Trade History    |
+----------+------------------------------+--------------------+
|  Order Form (Buy/Sell, Market/Limit/Stop Loss/Take Profit)   |
+--------------------------------------------------------------+
|  Open Orders table (ticker, side, type, price, qty, cancel)  |
+--------------------------------------------------------------+
\end{verbatim}

\subsection{Candlestick Chart (\texttt{components/Chart.tsx})}

The chart uses TradingView's Lightweight Charts library. It fetches data
from \texttt{GET /api/v1/candles/\{ticker\}/\{interval\}/200} and renders a
candlestick series. An interval selector lets the user switch between
1m, 5m, 15m, 1h, and 1d granularities.

\subsection{Order Form (\texttt{components/OrderForm.tsx})}

Supports all four order types with validation:
\begin{itemize}
\item Buy/Sell toggle button group
\item Market, Limit, Stop Loss, Take Profit selector
\item Conditional price input (required for Limit/Stop/Take Profit)
\item Quantity input with minimum validation
\item Real-time reference price display
\end{itemize}

\section{Auth Flow}

The React app uses \texttt{AuthContext} (stored in React state with
sessionStorage persistence). The protected route wrapper
(\texttt{ProtectedRoute}) redirects unauthenticated users to the login page:

\begin{lstlisting}[language=Java, caption=Protected route logic]
function ProtectedRoute({ children }: { children: React.ReactNode }) {
  const { sessionId, loading } = useAuth();
  if (loading) return <Loading />;
  if (!sessionId) return <Navigate to="/login" replace />;
  return <>{children}</>;
}
\end{lstlisting}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Configuration}
% ══════════════════════════════════════════════════════════════════════════════

All stock market configuration lives in \texttt{plugins/Market/config.yml}
under the \texttt{stock-api} key:

\begin{lstlisting}[language=sh, caption=config.yml stock-api section]
# Stock Market API -- embedded HTTP server + WebSocket
stock-api:
  # Enable the embedded servers for stock market website integration
  enabled: true
  # Port the HTTP REST API server listens on
  port: 8080
  # Port the WebSocket real-time server listens on
  ws-port: 8081
  # Rate-limiting: max requests per window for REST API
  rate-limit:
    max-requests: 120
    window-seconds: 60
\end{lstlisting}

\section{Port Configuration}

\begin{description}
\item[port (default 8080)] The REST API server. The Vite dev server proxies
  \texttt{/api/*} to this port.
\item[ws-port (default 8081)] The WebSocket server. The frontend connects
  directly to \texttt{ws://hostname:8081}.
\end{description}

\section{Rate Limiting}

\begin{description}
\item[max-requests (default 120)] Maximum number of REST API requests allowed
  within the window. Public endpoints are keyed by IP; authenticated endpoints
  are keyed by session UUID.
\item[window-seconds (default 60)] The sliding window duration in seconds.
\end{description}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Building and Deployment}
% ══════════════════════════════════════════════════════════════════════════════

\section{Prerequisites}

\begin{itemize}
\item Java 21 JDK (for the Spigot plugin)
\item Maven 3.8+ (for building the plugin)
\item Node.js 20+ and npm (for the frontend)
\item A Spigot/Paper 1.21.x Minecraft server
\end{itemize}

\section{Building the Plugin}

\begin{lstlisting}[language=sh, caption=Build plugin]
cd CN-Market-main
mvn clean package
\end{lstlisting}

The output JAR (\texttt{target/Market.jar}) is a shaded plugin containing
all dependencies.

\section{Running the Frontend}

\begin{lstlisting}[language=sh, caption=Start frontend dev server]
cd stock-website
npm install
npm run dev
\end{lstlisting}

The Vite dev server runs on port 3000 and proxies \texttt{/api/*} to
\texttt{localhost:8080} and \texttt{/ws} to \texttt{ws://localhost:8081}.

\section{Production Build}

\begin{lstlisting}[language=sh, caption=Production frontend build]
cd stock-website
npm run build
\end{lstlisting}

The output is in \texttt{stock-website/dist/} and can be served by any
static file server.

\section{Production Deployment (nginx)}

A reverse proxy is required in production so that the REST API
(\textasciitilde:8080), WebSocket (\textasciitilde:8081), and static frontend
are all served on the same origin. A reference config is provided in
\texttt{nginx-market.conf}:

\begin{lstlisting}[language=sh, caption=Deploy with nginx]
# 1. Build the plugin JAR and frontend dist
mvn clean package
cd stock-website && npm run build && cd ..

# 2. Copy artifacts to server
cp target/Market.jar /srv/minecraft/plugins/
cp -r stock-website/dist/* /var/www/market/

# 3. Install nginx config
sudo cp nginx-market.conf /etc/nginx/sites-available/market
sudo ln -s /etc/nginx/sites-available/market /etc/nginx/sites-enabled/
sudo nginx -t && sudo systemctl reload nginx
\end{lstlisting}

The nginx config handles:
\begin{itemize}
\item Static file serving from \texttt{/var/www/market} (with long-lived cache
  headers for \texttt{/assets/})
\item Reverse proxy for \texttt{/api/*} to \texttt{localhost:8080}
\item WebSocket upgrade for \texttt{/ws} to \texttt{localhost:8081}
\item SPA fallback (all routes serve \texttt{index.html})
\item Gzip compression and security headers
\end{itemize}

\section{Docker Test Server}

A \texttt{docker-compose.yml} is provided for local integration testing:

\begin{lstlisting}[language=sh, caption=Start Docker test server]
# Build the plugin first
mvn clean package

# Start PaperMC server with plugin mounted
docker compose up -d

# Watch server logs
docker compose logs -f mc-server
\end{lstlisting}

The Docker setup uses \texttt{itzg/minecraft-server} with Paper 1.21.x
(version 26.1.2) and mounts \texttt{target/Market.jar} into the plugins
directory.

\section{Testing with Injected Trades}

\begin{enumerate}
\item Start the Minecraft server with the plugin.
\item Generate an API key: \texttt{/market apikey generate}.
\item Inject test data: \texttt{/market admin stock inject DIAMOND 150.25 10}.
\item Open \texttt{http://localhost:3000}, paste the key, complete TOTP setup.
\item View the dashboard with injected trade data visible on the chart.
\end{enumerate}

% ══════════════════════════════════════════════════════════════════════════════
\chapter{Complete Source Listings}
% ══════════════════════════════════════════════════════════════════════════════

\section{Key File Reference}

\begin{longtable}{ll}
\toprule
\textbf{File} & \textbf{Lines} \\
\midrule
\endhead
\texttt{stock/StockMarketEngine.java} & 1019 \\
\texttt{stock/EmbeddedServer.java} & 798 \\
\texttt{stock/WebSocketManager.java} & 434 \\
\texttt{stock/ApiKeyManager.java} & 328 \\
\texttt{stock/TwoFactorAuth.java} & 180 \\
\texttt{stock/CandleAggregator.java} & 195 \\
\texttt{stock/RateLimiter.java} & 65 \\
\texttt{stock/transform.ts (frontend)} & 15 \\
\texttt{subcommands/StockCommand.java} & 38 \\
\texttt{subcommands/stock/Pause.java} & 56 \\
\texttt{subcommands/stock/Resume.java} & 51 \\
\texttt{subcommands/stock/Inject.java} & 88 \\
\texttt{subcommands/stock/Status.java} & 78 \\
\texttt{subcommands/ApiKeyCommand.java} & 42 \\
\texttt{subcommands/apikey/Generate.java} & 60 \\
\texttt{subcommands/apikey/Renew.java} & 48 \\
\texttt{subcommands/apikey/Revoke.java} & 48 \\
\texttt{subcommands/apikey/Status.java} & 58 \\
\texttt{managers/DatabaseManager.java} & 957 \\
\texttt{Market.java} & 182 \\
\texttt{nginx-market.conf} & 52 \\
\bottomrule
\end{longtable}

\section{Total Size}

\begin{itemize}
\item Java source (stock package): \textasciitilde3,250 lines
\item Java source (all stock-related): \textasciitilde4,600 lines
\item TypeScript/React source: \textasciitilde1,200 lines
\item Total: \textasciitilde5,800 lines of new code
\end{itemize}

\end{document}
